\emph{On Logics Extended with Embedding-Closed Quantifiers}

### 2020-10-06 paper.tex
Remove trailing spaces
Remove commented out sections
Update author contact info
Shorten the lines

%\title{On logics extended with embedding-closed quantifiers}
%%\date{}
%%\author{J. Haigora \and K. Luosto}
%\author[uta]{J.~Haigora\corref{cor1}}
%\ead{jevgeni.haigora@uta.fi}
%
%\author[uta]{K.~Luosto}
%\ead{kerkko.luosto@uta.fi}
%
%\address[uta]{University of Tampere, School of Information Sciences, FI-33014, Tampere, Finland}
%
%%\cortext[cor1]{Corresponding author}

@@

	\author{\fnms{Jevgeni}
		\snm{Haigora}
		\corref{}
		\ead[label=e1]{Haigora.Jevgeni.X@student.uta.fi}
	}
	\address{School of Information Sciences \\
		University of Tampere \\
		FI-33014, Tampere\\
		FINLAND\\
		\printead{e1}\\
	}
	\and 
	\author{\fnms{Kerkko}
		\snm{Luosto}
		\ead[label=e2]{Kerkko.Luosto@uta.fi}
	}
	\address{School of Information Sciences \\
		University of Tampere \\
		FI-33014, Tampere\\
		FINLAND\\
		\printead{e2}\\
	}
	\runauthor{J.~Haigora and K.~Luosto}

@@

%\begin{keyword}
%	Generalized quantifiers \sep  Embeddings \sep Ehrenfeucht-Fra\"iss\'e games
%	\MSC[2010] 03C80
%\end{keyword}

@@

%\maketitle

@@

A class $K$ of $\tau$-structures is \emph{embedding-closed} if $\mathfrak{A} \in K$ and $\mathfrak{A} \leq \mathfrak{B}$ imply $\mathfrak{B} \in K$. We say that a quantifier $Q$ is embedding-closed if its defining class is embedding-closed.
We denote by $\mathcal{Q}_{\emb}$ the class of all embedding-closed quantifiers.

\end{definition}

@@

Another nice feature of our method is that it can 
be applied to 
a wider range of logics that may have infinitely many embedding-closed quantifiers  
of arbitrary width. 
Thus we will show that, for instance, equicardinality of unary predicates in the class of all structures cannot be defined in $\mathcal{L}_{\infty \omega}(\mathcal{Q}_{\emb})$.

@@

\begin{lemma}\label{substr}
Let $\tau$ be a finite vocabulary and $\mathfrak{A}$ a finite $\tau$-structure.
Then the following holds:
\begin{enumerate}
\item There is a sentence $\varphi \in \mathcal{L}_{\omega\omega}[\tau]$ such that
for all $\mathfrak{B}\in \Str[\tau]$ we have
$\mathfrak{B} \vDash \varphi$ if and only if $\mathfrak{A} \leq \mathfrak{B}$.
%\[
%	\mathfrak{B} \vDash \varphi \text{ if and only if } \mathfrak{A} \leq \mathfrak{B}.
%\]
\item There is a sentence $\psi \in \mathcal{L}_{\omega\omega}[\tau]$ such that
$\mathfrak{B} \vDash \psi$ if and only if $\mathfrak{B}$ is isomorphic to $\mathfrak{A}$.
\end{enumerate} 
\end{lemma}

@@

%\begin{thebibliography}{99}
%\bibitem{Cherlin: 1986}G. Cherlin, A. H. Lachlan, Stable finitely homogeneous structures, Trans. Amer. Math. Soc, 296 (2) (1985) 815-850. 
%\bibitem{Cherlin: 2000}G. Cherlin, U. Felgner, Homogeneous finite groups, Journal of the London Mathematical Society, 62 (3) (2000) 784-794.
%\bibitem{Dawar: 2010}A. Dawar, E. Gr\"adel, Properties of almost all graphs and generalized quantifiers, Fundamenta Informaticae, 98 (1) (2010) 351-372.
%\bibitem{Ebbinghaus: 1985} H-D. Ebbinghaus, Extended logics: the general framework, Model-theoretic logics (J. Barwise and S. Feferman, editors), Springer-Verlag, Berlin, (1985) 25-76.
%\bibitem{Fagin: 1976} R. Fagin, Probabilities on finite models,  J. Symbolic Logic, 41 (1) (1976) 50-58.
%\bibitem{Friedman: 1973} H. Friedman, Beth's theorem in cardinality logics, Israel J. Math, 14 (1973), 205-212. 
%\bibitem{Gardiner: 1976} A. Gardiner, Homogeneous graphs, J. Combinatorial Theory Ser. B, 20 (1) (1976) 94-102.
%\bibitem{Glebskii: 1969}  Y. V. Glebskii, D. I. Kogan, M. I. Liogon'kii, V. A. Talanov, Range and degree of realizability of formulas in the restricted predicate calculus, Cybernetics, 5 (1969) 142-154. 
%\bibitem{Gregory: 1974} J. Gregory, Beth definability in infinitary languages, J. Symbolic Logic, 39 (1) (1974) 22-26.
%\bibitem{Hella: 1984} L. Hella, Definability hierarchies of generalized quantifiers,  Ann. Pure Appl. Logic, 43 (3) (1989) 235-271.
%\bibitem{Keisler: 2011} H. J. Keisler, W. B. Lotfallah, Rank hierarchies for generalized quantifiers, J. Log. Comput, 21 (2) (2011) 287-306.
%\bibitem{Lachlan: 1984}A. H. Lachlan, On countable stable structures which are homogeneous for a finite relational language, Israel J. Math, 49 (1-3) (1984) 69-153.
%\bibitem{Lachlan: 1986} A. H. Lachlan, Homogeneous structures, Proc. of the ICM, (1986) 314-321.
%\bibitem{Lindstrom: 1966}P. Lindstr\"om, First order predicate logic with generalized quantifiers. Theoria, 32 (1966) 186-195.
%\bibitem{Makowski: 1979} J. A. Makowski, S. Shelah, The theorems of Beth and Craig in abstract model theory, I: The abstract setting.  Trans. Amer. Math. Soc., 256 (1979) 215-239. 
%\bibitem{Mostowski: 1957}A. Mostowski, On a generalization of quantifiers.  Fund. Math., 44 (1957) 12-36.
%\bibitem{Saracino: 1988}D. Saracino, C. Wood, Homogeneous finite rings in characteristic $2^n$,  Ann. Pure Appl. Logic, 40 (1) (1988) 11-28.
%\end{thebibliography}
\end{document}

>>>>

@@

	\author{\fnms{Jevgeni}
		\snm{Haigora}
		\corref{}
		\ead[label=e1]{jhaigora@gmail.com}
	}
	\address{
		\printead{e1}\\
	}
	\and
	\author{\fnms{Kerkko}
		\snm{Luosto}
		\ead[label=e2]{Kerkko.Luosto@tuni.fi}
	}
	\address{Faculty of Information Technology and Communication Sciences \\
	  Computing Sciences \\
		Tampere University \\
		FI-33014, Tampere\\
		FINLAND\\
		\printead{e2}\\
	}
	\runauthor{J.~Haigora and K.~Luosto}

@@

@@

@@

A class $K$ of $\tau$-structures is \emph{embedding-closed} if
$\mathfrak{A} \in K$ and $\mathfrak{A} \leq \mathfrak{B}$ imply
$\mathfrak{B} \in K$. We say that a quantifier $Q$ is embedding-closed if its
defining class is embedding-closed.
We denote by $\mathcal{Q}_{\emb}$ the class of all embedding-closed quantifiers.
\end{definition}

@@

Another nice feature of our method is that it can be applied to a wider range of
logics that may have infinitely many embedding-closed quantifiersmof arbitrary
width.
Thus we will show that, for instance, equicardinality of unary predicates in the
class of all structures cannot be defined in
$\mathcal{L}_{\infty \omega}(\mathcal{Q}_{\emb})$.

@@

\begin{lemma}\label{substr}
Let $\tau$ be a finite vocabulary and $\mathfrak{A}$ a finite $\tau$-structure.
Then the following holds:
\begin{enumerate}
\item There is a sentence $\varphi \in \mathcal{L}_{\omega\omega}[\tau]$ such
that for all $\mathfrak{B}\in \Str[\tau]$ we have
$\mathfrak{B} \vDash \varphi$ if and only if $\mathfrak{A} \leq \mathfrak{B}$.
\item There is a sentence $\psi \in \mathcal{L}_{\omega\omega}[\tau]$ such that
$\mathfrak{B} \vDash \psi$ if and only if $\mathfrak{B}$ is isomorphic to
$\mathfrak{A}$.
\end{enumerate}
\end{lemma}

@@

\end{document}
